\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
  \parsep=0in
% if using pdflatex:
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

  \newenvironment{list1}{
    \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
        \setlength{\parsep}{0in} \setlength{\parskip}{0in}
        \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
    \setlength{\leftmargin}{0.17in}}}{\end{list}}
    \newenvironment{list2}{
      \begin{list}{$\bullet$}{%
        \setlength{\itemsep}{0in}
          \setlength{\parsep}{0in} \setlength{\parskip}{0in}
          \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


      \begin{document}

      \name{{\bf Eric Buckthal} \vspace*{.1in}}

      \begin{resume}
        \section{\sc Contact Information}
        \vspace{.05in}
        \begin{tabular}{@{}p{2in}p{4in}}
          390 Islay Street           & (208) 841-0115\\
          San Luis Obispo, CA 93401  & {\tt ebucktha@calpoly.edu} \\
        \end{tabular}

        \section{\sc Education}
        {\bf California Polytechnic State University}, San Luis Obispo, California\\
        \vspace*{-.1in}
        \begin{list1}
        \item[] Master of Science {\bf Computer Science}, expected June 2013
%\begin{list2}
%\vspace*{.05in}
%\item Dissertation Topic:  ``Nonstationary Covariance Models for
%  Spatial Data and Regression Problems''
%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.''
%\item Advisor:  Mark J. Schervish
%\end{list2}
          \vspace*{.05in}
        \item[] Bachelor of Science {\bf Computer Engineering}, expected June 2013
        \end{list1}

        \section{\sc Technical Projects}
        {\bf Robotic Arm Pendant Controller} \hfill {\em September 2011 - March 2012}\\
        \begin{list2}
        \item Team-oriented sponsored project (Strasbaugh, San Luis Obispo) to redesign dated user interface pendant for laptop support while overhauling automation and servo control. 
        \item Re-engineered Staubli robotic arm to interface with {\sc EtherCAT} automation protocol. Server implementation managed a networked controlling client and communicated via {\sc TwinCAT} Suite with Staubli robot.
        \end{list2}

        {\bf Sliding Window Remote File Duplication} \hfill {\em December 2011}\\
        C implementation of packet delivery from server to client over local network, including ability to manage multiple clients with pthreading. The project highlighted transport level selective rejection ARQ to handle induced packet loss and corruption.
        \vspace*{.05in}

        {\bf Real-time Network Distribution of Graphical Data} \hfill {\em March 2012}\\
        Cost-performance analysis of the distribution of real-time graphical data across multiple physics engines, rendering on a central client. My team experimented with the capabilities of TCP, intending to off-load expensive physics calculations to a remote server while maintaining a responsive host. The overhead associated with networked data demonstrated low scalability.
        \vspace*{.05in}

        {\bf Algorithm Analysis} \hfill {\em January 2012 - March 2012}\\
        Investigated algorithmic complexity by designing solutions to practical problems with dynamic programming, branch-and-bound, divide-and-conquer, linear programming, and greedy approaches. Projects reinforced Java, object-oriented programming, and tests-before-design technique.
        \vspace*{.05in}

        \section{\sc Professional Experience}
        {\bf Cygnet Software}, San Luis Obispo, California

        \vspace{-.3cm}
        {\bf Software Developer Internship} \hfill {\em June 2011 - September 2011}\\
        Designed and implemented unit-testing applications and projects graphing certain data for SCADA Suite. Majority of the work done in partners within a larger group of interns; we engineered C++ MFC applications, with various work in Visual Basic.

        {\bf Computer Networks Laboratory}, California Polytechnic State University

        \vspace{-.3cm}
        {\em Teaching Assistant} \hfill {\em January 2012 - Present}\\

        \section{\sc Leadership and Involvement}
        \begin{list1}
        \item[] {\bf Tau Beta Pi}, California Mu Chapter \hfill {\em Active Member}
        \item[] {\bf Eta Kappa Nu}, Epsilon Phi Chapter \hfill {\em Active Member}
        \item[] {\bf KCPR} Cal Poly Radio Station
          \begin{list2}
          \item[] Program Director \hfill {\em April 2011 - April 2012}
          \item[] Music Director \hfill {\em April 2012 - Present}
          \end{list2}
        \end{list1}

%\section{\sc Computer Skills}
%\begin{list2}
%\item Statistical Packages:  R, S-Plus, BUGS; some experience
%  with SAS; extensive use of C and Fortran statistical libraries.
%\item Languages:  C++, Perl, Pascal, some use of Unix shell scripts,
%  MPI parallel processing library.
%\item Applications: Generic Mapping Tools (GMT) - Unix mapping software, \LaTeX, common %Windows
%  database, spreadsheet, and presentation software
%\item Algorithms: Experience programming Markov Chain Monte Carlo
%  simulations of Bayesian posterior distributions
%\item Operating Systems:  Unix/Linux, Windows.\\
%\end{list2}

      \end{resume}
      \end{document}



